%For decades~\cite{PhysRev.81.165}, it has been known that the nucleon-nucleon potential has a short-range repulsive core, which is responsible for the stability of strongly interacting matter. However, a description of the repulsive core remains largely unconstrained and our understanding of QCD dynamics at short distances ($\leq 0.5\mathrm{~fm}$) largely incomplete~\cite{Sargsian:2014bwa}. 

The deuteron is the simplest composite nuclear system, and in many ways it is as important to understanding bound states in QCD as the hydrogen atom was to understanding bound systems in QED.  However, our experimental and theoretical understanding of the deuteron at short distances remains unsatisfactory. A well-constrained theoretical description is essential for understanding the dynamics of short-range NN correlations in nuclei, which are dominated by tensor interactions up to 700~MeV/$c$ internal momenta.

%Our experimental and theoretical understanding of the deuteron remains unsatisfying, which we will address by measuring the tensor asymmetry $A_{zz}$ for the first time in a kinematic region where theoretical understanding of the deuteron is weak.

It has been known for many years that that in addition to the $L = 0$ (S-state) component of the ground state of the deuteron, there is also present at the $4-7\%$ percent level, an $L = 2$ (D-state) component. In 1939, Schwinger pointed out that the quadrupole moment of the deuteron provided irrefutable evidence for a tensor component of the nuclear force. The tensor force doesn't conserve either the spin ($S$) or the orbital angular momentum ($L$), but only the total angular momentum ($J$), therefore allowing mixing between the predominant spherically symmetric $S$ state and configurations with the $L = 2$ D-state.


Tensor polarization enhances the D-state contribution, which compresses the deuteron~\cite{Forest:1996kp}, 
%in a toroid as shown in Fig.~\ref{fig:dpol-shape}, 
making the system more sensitive to short-range effects. 
%Due to their small size and simple structure, tensor polarized deuterons are ideal for studying nucleon-nucleon interactions at short distances. 
Understanding the short distance nucleon-nucleon potential of the deuteron is essential for understanding short-range correlations, as they are largely dependent on the tensor force~\cite{Arrington:2011xs}. Both inclusive and exclusive electron scattering at $x>1$ have revealed the strength of short range correlations and their isospin dependence at large momenta ($p>k_f$)~\cite{Korover:2014dma}, which is well supported by theory~\cite{Schiavilla:2006xx}. We can resolve the short-range structure of nuclei on the level of nucleon and hadronic constituents by utilizing processes that transfer both energy and momentum larger than the scale of the NN short-range correlations to the nucleon constituents, particularly at $Q^2>1~(\mathrm{GeV}/c)^2$.





By taking a ratio of cross sections from electron scattering from tensor-polarized and unpolarized deuterons, 
\begin{equation}
A_{zz}=\frac{2}{fP_{zz}}\left(\frac{\sigma_p}{\sigma_u}-1\right),
\end{equation}
the S and D-wave states can be disentangled, leading to a fuller understanding of the attractive and repulsive components of the nucleon core. A measurement of $A_{zz}$ is sensitive to the ratio $\frac{D^2-SD}{S^2+D^2}$ and its evolution with increasing minimal momentum of the struck nucleon. 

Within the past few years, there has been a strong theoretical effort to better understand the deuteron through the quasi-elastic $A_{zz}$ observable. First calculated in 1970's to demonstrate its usefulness in probing the short-range nuclear core in the region where the D-state dominates~\cite{Frankfurt:1988nt}, it has recently been revisited by M.~Sargsian and M.~Strikman who have calculated $A_{zz}$ in the $x > 1$ range using relativistic light-cone and virtual-nucleon methods~\cite{Sargsian:2014fla}. For quasi-elastic $A_{zz}$, these methods differ by up to a factor of two and can be discriminated experimentally at the $3-6\sigma$ level. Probing these relativistic models is crucial for advancing our understanding of short range correlations, which are dominated by tensor interactions~\cite{Korover:2014dma}. Additionally, the calculations are sensitive to the S/D ratio of the input deuteron wave functions at large relative momenta $k>300$~MeV, which show a large discrepancy at high $x$ and can be used to further the original intent of $A_{zz}$ to discriminate between soft and hard $pn$ potentials. 

%Originally calculated by L.~Frankfurt and M.~Strikman~\cite{Frankfurt:1988nt}, this has recently been revisited by M.~Sargsian and M.~Strikman, who calculated $A_{zz}$ in this region using light cone and virtual nucleon approaches with multiple NN potentials~\cite{Sargsian:2014fla}. The results vary by up to a factor of 2, and can be experimentally determined at the $3-6\sigma$ level as discussed here. In this same region, effects from final state interactions have been calculated and are expected to have a significant effect at large $x$~\cite{cosyn-convo}.


%For the lower $Q^2$ region, W. Van Orden has calculations in progress using different nucleon-nucleon potentials, as well as different prescriptions for handling the reaction mechanisms in tensor polarization observables in the low $Q^2$ region~\cite{vanorden-convo}. Although it is difficult to disentangle reaction mechanisms from NN potentials using cross section measurements, previous low $Q^2$ results have indicated that asymmetries are far less sensitive to the reaction mechanisms~\cite{Passchier:2001uc}. Similar calculations have also been finalized for the D($e,e'p)n$ at high $Q^2$, high $p_m$ experiment~\cite{Ford:2014yua}. 

A number of other theoretical efforts have begun to further use $A_{zz}$ to understand the simplest composite nuclear system. Effects from final state interactions have been calculated using a virtual nucleon model with various NN potentials by W.~Cosyn, and are expected to have a significant effect on $A_{zz}$ at large $x$ and must be understood to probe nucleonic effects. Calculations on 6-quark effects in the elastic region are being calculated by G.A. Miller. Calculations from W. Van Orden are in progress for the low $Q^2$ region using different nucleon-nucleon potentials, as well as different prescriptions for handling the reaction mechanisms in tensor polarization observables~\cite{vanorden-convo}. Although it is difficult to disentangle reaction mechanisms from NN potentials using cross section measurements, previous low $Q^2$ results have indicated that asymmetries are far less sensitive to the reaction mechanisms~\cite{Passchier:2001uc}. Similar calculations have also been finalized for the D($e,e'p)n$ at high $Q^2$, high $p_m$ experiment~\cite{Ford:2014yua}. 



Measuring $A_{zz}$ in the quasi-elastic region will fill a gap in measurements performed on deuterium scattering. It is directly proportional to the elastic deuteron tensor analyzing powers by $A_{zz} = \sqrt{2} \left[ d_{20} T_{20} + d_{21} T_{21} + d_{22} T_{22}\right]$. 
%Due to the large acceptance of the SHMS spectrometer, we will be taking data in the $x = 2$ elastic range as well, allowing us to measure $T_{20}$ in a large range of $Q^2$ (as contributions from $T_{21}$ and $T_{22}$ are small). 
In the deep inelastic region, $A_{zz}$ will soon be measured to extract the tensor structure function $b_1$ by the relation $A_{zz} \propto \frac{b_1}{F_1^D}$. Not only will measuring $A_{zz}$ in the quasi-elastic region provide information necessary for understanding the fundamental properties of the deuteron, it will be the first experiment to bridge a gap in measurements of electron scattering from tensor-polarized deuterons. We emphasize that this measurement is pushing the limits of understanding the deuteron by going to kinematics where no current measurements exist and where current theoretical understanding remains unsatisfying.



